SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-19 paper/encoding.tex
added
update

@@

We use two Boolean variables A0 and A1 to build these two constraints. \newline

A0: No regulation on nodes i.e all the present molecules on the nodes are active.
\[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]

A0: Boolean regulation on nodes. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]

A1: No regulation on edges i.e all the present molecules on the edges are active.
\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]

A1: Boolean regulation on edges. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e_{i,j,q,k'}) \, \]

A1: Pairing inhibition. The activity of the molecules is defined by inhibition by other molecules based on the pairing matrix. 
\[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]

>>>>

\subsection{Model}

\begin{df}
  A VTS $G$ consists of ...... most general model 
\end{df}

Variants of the model : restrictions...

formal definition of the properties in the terms of VTS.

State the SAT problem

\subsection{Boolean satisfiability of the problem}

@@

We use two Boolean variables A\_* to build these two constraints. \newline

A\_nn: No regulation on nodes i.e all the present molecules on the nodes are active.
\[ \bigwedge\limits_{i,k} n_{i,k} == a_{i,k} \, \]

A\_nb: Boolean regulation on nodes. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
\[ \bigwedge\limits_{i,k} n_{i,k} \supset a_{i,k} ==   f_n[k] (\bigvee_{ k' != k} n_{i,k'}) \, \]

A\_en: No regulation on edges i.e all the present molecules on the edges are active.
\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} == b_{i,j,q,k} \, \]

A\_eb: Boolean regulation on edges. Activity of a molecule k on the node is defined as a Boolean function of presence of other molecule present on that node.
\[ \bigwedge\limits_{i,j,q,k} e_{i,j,q,k} \supset b_{i,j,q,k} == f_e[k](\bigvee_{k' != k} e_{i,j,q,k'}) \, \]

A\_ep: Pairing inhibition. The activity of the molecules is defined by inhibition by other molecules based on the pairing matrix. 
\[ \bigwedge\limits_{i,j,q, k}  (e_{i,j,q,k} \land [ ( \bigvee_{k'} p_{k,k'} \land \bigwedge_{k' != k} p_{k,k'} \supset e_{i,j,q,k'})] ) \supset \neg b_{i,j,q,k}) \, \]
